Supplementary Material for _A Guide to Pre-processing High-Frequency Animal Tracking Data_

### 2021-10-04 supplement/06_bat_data.Rmd
get mean and sd night and distance roost

# split the data
data_residence <- split(data_residence, data_residence$TAG)
```

@@

```{r}
# segment into residence patches
data_patches <- lapply(data_residence, atl_res_patch,
  buffer_radius = 25,
  min_fixes = 3
)
```

>>>>

# split the data
data_residence <- split(data_residence, by = c("TAG", "night"))
```

@@

```{r}
# segment into residence patches
data_patches <- lapply(data_residence, atl_res_patch,
  buffer_radius = 25,
  min_fixes = 3,
  summary_variable = c("night", "distance_roost"),
  summary_functions = c("mean", "sd")
)
```
